Stack Safety as a Security Property

### 2020-07-07 main.tex

For example, consider the unsafe substitution:
\[
42 : ~ \sw ~ r_4 ~ \rsp 100
\]
Instead of reading the proper argument, {\tt h} reads directly from the
secret value of {\tt x} that belongs to {\tt main}. \Cref{fig:confex}
shows \(\mach_e\), the entry state of {\tt h}, with high confidentiality memory
in red and low confidentiality in green. Below it, the variant state
\(\mach_e'\) agrees on low confidentiality memory, but the rest might have
any value, in yellow. After the last step, the return states \(\mach_r\) and
\(\mach_r'\) should agree on every component that changed since \(\mach_e\) or
\(\mach_e'\). Addresses 108 and 109 have changed, shown in pink, and while 109
is consistent, 108 will not hold 43 in all variants, so the trace does not obey
trace confidentiality.
\rb{Color name macros}

>>>>

For example, consider the unsafe substitution:
\[
42 : ~ \sw ~ r_4 ~ \rsp 100
\]
Instead of reading the proper argument, {\tt h} reads directly from the
secret value of {\tt x} that belongs to {\tt main}. \Cref{fig:confex}
shows \(\mach_e\), the entry state of {\tt h}, with high confidentiality memory
in magenta and low confidentiality in teal. Below it, the variant state
\(\mach_e'\) agrees on low confidentiality memory, but all other addresses
hold -5, in orange. After the last step, the return states \(\mach_r\) and
\(\mach_r'\) should agree on every component that changed since \(\mach_e\) or
\(\mach_e'\). Addresses 108 and 109 have changed, shown in gray, and while 109
is consistent, 108 holds either 43 or -4, so the trace does not obey
trace confidentiality.
\rb{Color name macros}

\sna{I like instantiating the variant, tomorrow I will extend it to the
     lazy example as well.}
